Estimating contemporary migration rates for iteroparous species using kinship pairs found between populations

### 2022-01-19 latex/ms.tex
filled letters in Discussion, #14

To estimate the contemporary migration number or migration rate, our simulation-based results provide guidance for a sample size to ensure the required accuracy and precision, especially if the order of the number of migrant parents and parental sizes are approximately known ({\bf Table S1} in {\bf Supporting Information}). Even if there is no information about these numbers, $1/\sqrt{H_{\rm HS, bet}}$ (or $1/\sqrt{H_{\rm PO, bet}}$) provides an approximate lower bound on the CV, which can be used as an indicator of the precision of ${\hat M}$ or ${\hat m}$. Furthermore, the condition that $n>\sqrt{N_2}$ is also used as rule of thumb especially when planning a research project (see also Equations~\ref{RS-1} and \ref{RS-2}).

@@

Finally, we note some caveats in applying proposed method. Our theory for developing estimators assumes that kinships are detected without any error. There are many algorithms to detect kinship pairs from single nucleotide polymorphisms (SNPs) or short tandem repeats (STRs) (\RED{REF}), although a HS pair requires many more DNA markers than a PO pair. In addition, iteroprous species potentially has several kinship types such as halfsib-uncle/nephew or halfsib-cousin, which are expected to appear frequently and should be correctly distinguished from HS pairs. It is desirable to estimate in advance how many markers are needed for kinship detections in target populations associated with simulation of a pedigree reconstruction including distant kinships (e.g., \cite{Anderson_2020}). Our proposed estimators only detect the parental movements on a period between breeding seasons in given populations.

%必要条件としては、個体数管理のため、細かすぎる時空かんスケールはだめ。大雑把なpopulationを仮定したい時に限る（空間的に細かいグリッドは困難？）、集団構造がspecifyされた後に実施される。繁殖タイミングの間隔の移動を統合したもの、子供の移動については何も言ってない。繁殖タイミングの間の移動しか捕捉できない。

\RED{kokomade!!!!!!!!!!!!!!!!!!!!}

>>>>

To estimate the contemporary migration number or migration rate, our simulation-based results provide guidance for a sample size to ensure the required accuracy and precision, especially if the order of the number of migrant parents and parental sizes are approximately known ({\bf Table S1} in {\bf Supporting Information}). \RED{For example, ...} Even if there is no information about these numbers, $1/\sqrt{H_{\rm HS, bet}}$ (or $1/\sqrt{H_{\rm PO, bet}}$) provides an approximate lower bound on the CV, which can be used as an indicator of the precision of ${\hat M}$ or ${\hat m}$. Furthermore, the condition that $n>\sqrt{N_2}$ is also used as rule of thumb especially when planning a research project (see also Equations~\ref{RS-1} and \ref{RS-2}).

@@

Finally, we note some caveats in applying proposed method. Our theory for developing estimators assumes that kinships are detected without any error. There are many algorithms to detect kinship pairs from single nucleotide polymorphisms (SNPs) or short tandem repeats (STRs) (\RED{REF}), although a HS pair requires many more DNA markers than a PO pair. In addition, iteroprous species potentially has several kinship types such as halfsib-uncle/nephew or halfsib-cousin, which are expected to appear frequently and should be correctly distinguished from HS pairs. It is desirable to estimate in advance how many markers are needed for kinship detections in target populations associated with simulation of a pedigree reconstruction including distant kinships (e.g., \cite{Anderson_2020}). Our proposed estimators are limited to detect one-time parental movements on a period between breeding seasons in given populations. Thus, the estimation of fine-scale spatial-temporal movements, which is available to integrate multiple type of data \cite[]{Thorson_2021}, goes beyond the scope of this paper, although population dynamics models with a coarser spatial resolution than the spatial scale for environmental layers are often used in the assessment models, which is the target of application of the proposed method. In addition, our proposed estimators require the pre-specification of a population structure. Kinship relationships with information of a sample location potentially provide the chance to explore a plausible population structure via estimating migration number or rate between hypothetical populations, which contributes the determination of a management unit \cite[]{Hastings_1993, Waples_2006_MolEcol, PALSBOLL200711}. This perspective of the study will be conducted in the future.

%必要条件としては、個体数管理のため、細かすぎる時空かんスケールはだめ。大雑把なpopulationを仮定したい時に限る（空間的に細かいグリッドは困難？）、集団構造がspecifyされた後に実施される。繁殖タイミングの間隔の移動を統合したもの、子供の移動については何も言ってない。繁殖タイミングの間の移動しか捕捉できない。事前に集団について割り当てておく必要がある。サンプルデザインを考えて、サンプル場所と見つかる近親関係を対応させて、管理単位の決定に寄与するような集団構造の探索は可能だろう。ヘイステングの方法などあるが、近親情報に基づいて、集団の単位を発見する理論的枠組みは、今後の課題である

%conn & bravington も引用しないと
